Instructions for ACL-2016 Proceedings

### 2016-05-23 paper.tex
paper.{bib,tex} - fix *unclear* status of deTenTen

\begin{table}[h]
\begin{center}
\begin{tabular}{l|r|r}
\hline
\multicolumn{1}{c}{}	& \multicolumn{1}{c}{Tokens}	& \multicolumn{1}{c}{Sentences} \\ \hline
empirist    			& $10*10^3$	& $0.6*10^3$      \\ \hline
Tiger v2.2 		& $0.9*10^9$	& $0.05*10^6$	  \\ \hline
de.wiki'15   		& $2.0*10^9$	& $79*10^6$	  \\ \hline\hline
C4Corpus            	& $$		& $$	  \\ \hline
DECOW14           	& $11.7*10^9$	& $600*10^6$	  \\ \hline
\emph{*unclear*}	& $19.9*10^9$	& $1300*10^6$	  \\ \hline
\end{tabular}
\end{center}
\caption{\label{tab:corpora}Training data used for EmpiriST (upper part) and additional data for the subsequent experiments (lower part).}
\end{table}

@@

\emph{*unclear*} web corpus.
%DeTenTen
% $19.9*10^9$ (19,918,263,493) tokens
% $1.3*10^9$ (1,309,696,220) sentences

@@

As additional data to train word embedding models we obtained and processed \emph{C4Corpus}, \emph{DECOW14}, and \emph{*unclear*}.

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{l|r|r}
\hline
\multicolumn{1}{c}{}	& \multicolumn{1}{c}{Tokens}	& \multicolumn{1}{c}{Sentences} \\ \hline
empirist    			& $10*10^3$	& $0.6*10^3$      \\ \hline
Tiger v2.2 		& $0.9*10^9$	& $0.05*10^6$	  \\ \hline
de.wiki'15   	& $2.0*10^9$	& $79*10^6$	  \\ \hline\hline
C4Corpus            	& $$		& $$	  \\ \hline
DECOW14         & $11.7*10^9$	& $600*10^6$	  \\ \hline
deTenTen	    & $19.9*10^9$	& $1300*10^6$	  \\ \hline
\end{tabular}
\end{center}
\caption{\label{tab:corpora}Training data used for EmpiriST (upper part) and additional data for the subsequent experiments (lower part).}
\end{table}

@@

\emph{deTenTen} web corpus.
%DeTenTen
% $19.9*10^9$ (19,918,263,493) tokens
% $1.3*10^9$ (1,309,696,220) sentences
\cite{1120431}

@@

As additional data to train word embedding models we obtained and processed \emph{C4Corpus}, \emph{DECOW14}, and \emph{deTenTen}.
